A general and efficient representation of Ancestral Recombination Graphs

### 2023-10-06 paper.tex
REmove "straw man" reference

Note that the \citet{wiuf1999recombination} eARG
in Fig.~\ref{fig-ancestry-resolution} is something of a straw man,
in that typically an inference or backward-time simulation program would only produce an
ARG containing
nodes or edges ancestral to the sample
(see the discussion of the ``Big ARG'' stochastic process in Appendix XXX,
however). Nonetheless, it
is an instructive example from the literature which highlights several
important properties of ARGs, and the general point about
the need to resolve ancestral material ``on the fly'' for eARG traversals
holds.

>>>>

Note that the \citet{wiuf1999recombination} eARG
in Fig.~\ref{fig-ancestry-resolution} is not particularly
representative, because inference or simulation methods will usually
only generate ARGs containing nodes and edges ancestral to the sample
(see the discussion of the ``Big ARG'' stochastic process in Appendix XXX, however).
Nonetheless, it is an instructive example from the literature which highlights several
important properties of ARGs, and the general point about
the need to resolve ancestral material ``on the fly'' for eARG traversals
holds.
